### Environment Load and Check

-   this code section is packaged as an include for reuse across all examples
-   it uses the HTML details tag directly to wrap code blocks and output as drop-down sections

<details>

<summary>Show Environment</summary>

```{r}
library(patchwork)
library(dplyr)
library(Seurat)
```

-   Is there a typo in the message above? Application Programming Interface, **API** != **ABI**

-   Rolling back to R 4.3.0 was not possible with the current version of Seurat

    -   the indication was that Seurat requires a version of base Matrix that is not present in R 4.3.0

```{r}
# which Seurat?
packageVersion("Seurat")
# which R?
version[['version.string']]

# presto was installed 
# For a (much!) faster implementation of the 
# Wilcoxon Rank Sum Test
packageVersion('presto')
```

```{python}
# check python is available via reticulate
import sys
print(sys.version.split(" ")[0])
```

```{bash}
# shell check
python3 -V
```

</details>

### Functions

<details>

<summary>Show Functions</summary>

```{r}
# Useful for code development.
# Save the object at a point and reload it into the R console 
# i.e. for developing alternative reports 
# without having to run the pipeline right from the start
# which can be slow
#
# NB: Files produced by saveRDS (or serialized to a file connection) 
# are not suitable as an interchange format between machines
# 
# For that use hdf5 or transfer data and code to reproduce the result 

saveRDS_overwrite <- function(file_path) {
  if (file.exists(file_path)) {
    file.remove(file_path)
  } 
  saveRDS(pbmc, file = file_path)
}

```

</details>
